An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-24 VLDB2026/main.tex
Update main.tex

		\footnotesize{
		\begin{center}
			\begin{minipage}{\linewidth}
				\centering	
				Note: \textit{Strong} represents robust to attribute distribution, \textit{Weak} represents sensitive to attribute distribution 
			\end{minipage}
		\end{center}
		}
	\end{figure*}

	\textit{\textbf{Multi-Attribute Building and Multi-Attribute Query.}}  
	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world scenarios. To evaluate algorithm performance under this setting, we construct the index using 3 uniformly distributed attributes and apply filtering on all 3 attributes simultaneously during queries. \textcolor{orange}{Note that FilterDiskANN only supports Boolean OR logic and does not support Boolean AND. Therefore, its two Vamana-based methods are excluded from the multi-attribute construction and search experiments.}
	%	\textcolor{red}{As Filtered-DiskANN does not support the AND rule used in our multi-attribute queries, it is excluded.}
	%	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world application scenarios. To evaluate algorithm performance under such scenario, we construct the index using 3 uniformly distributed attributes and apply filtering conditions on all 3 attributes simultaneously during the query process.

@@

	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
	\textcolor{cyan}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on Server B using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}. Compared with the experimental results on Server A shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}f, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations. Due to the lower CPU frequency and smaller RAM capacity of Server B compared to Server A, the QPS values are slightly lower across all methods.}
%	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}. Compared with the experimental results on the original server (as shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}(f)), the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations. Due to the lower CPU frequency of the Xeon 6330 compared to the original server, the QPS values are slightly lower across all methods.}

@@

	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}}
	\textcolor{cyan}{As described in Section 4.2.4, we performed additional range filtering experiments using the YT-Audio-Real dataset on Server B, with results presented in Figure~\ref{fig:Different_Computer_range}. When compared with the experimental results of Server A shown in Figure~\ref{fig:exp_8_2}a, our findings remain consistent with those reported in Section 4.2.4. For brevity and due to space limitations, we omit further discussion of these redundant results.}
%	\textcolor{cyan}{Consistent with Section 4.2.4, we conducted additional range filtering experiments using the YT-Audio-Real dataset on the same server, with results shown in Figure \ref{fig:Different Computer range}. Compared with the original server's experimental results (Figure \ref{fig:exp_8_2}($e$)), the conclusions remain identical to those described in Section 4.2.4. Due to space constraints, these details are not reiterated here.}

>>>>

		\footnotesize{
		\begin{center}
			\begin{minipage}{\linewidth}
				\centering	
				\textit{Strong} : robust to attribute distribution shifts,  \textit{Weak} : sensitive to attribute distribution shifts
			\end{minipage}
		\end{center}
		}
	\end{figure*}

	\textit{\textbf{Multi-Attribute Building and Multi-Attribute Query.}}  
	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world scenarios. To evaluate algorithm performance under this setting, we construct the index using 3 uniformly distributed attributes and apply filtering on all 3 attributes simultaneously during queries. \textcolor{orange}{In this experiment, we only evaluate the algorithms that support this query scenario.}
	%	\textcolor{red}{As Filtered-DiskANN does not support the AND rule used in our multi-attribute queries, it is excluded.}
	%	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world application scenarios. To evaluate algorithm performance under such scenario, we construct the index using 3 uniformly distributed attributes and apply filtering conditions on all 3 attributes simultaneously during the query process.

@@

	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
%	\textcolor{cyan}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on Server B using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}. Compared with the experimental results on Server A shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}f, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations. Due to the lower CPU frequency and smaller RAM capacity of Server B compared to Server A, the QPS values are slightly lower across all methods.}
	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}. Compared with the experimental results on the original server (as shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}(f)), the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations. Due to the lower CPU frequency and smaller RAM capacity, the QPS values are slightly lower across all methods.}

@@

	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}}
	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:Different_Computer_range}. When compared with the experimental results of the original server shown in Figure~\ref{fig:exp_8_2}a, our findings remain consistent with those reported in Section 4.2.4. For brevity and due to space limitations, we omit further discussion of these redundant results.}
%	\textcolor{cyan}{Consistent with Section 4.2.4, we conducted additional range filtering experiments using the YT-Audio-Real dataset on the same server, with results shown in Figure \ref{fig:Different Computer range}. Compared with the original server's experimental results (Figure \ref{fig:exp_8_2}($e$)), the conclusions remain identical to those described in Section 4.2.4. Due to space constraints, these details are not reiterated here.}
